### 2018-01-16 Documents/bootcamp_syllabus.tex
Updated Spring 2018 Syllabus

%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp}
\runningheader{Data Bootcamp}{}{Syllabus: ECON-UB.0011.02}
\runningfooter{}{}{}

\begin{document}
\centerline{\Large\bf Syllabus:  Data Bootcamp}
\vspace{3mm}
\centerline{\large\bf ECON-UB.0232 $|$ Fall 2017}
\vspace{3mm}
\centerline{\bf Revised:  \today}

@@

\subsubsection*{About the Instructor}
\href{http://www.waugheconomics.com}{Professor Michael Waugh} \\
Email: \href{mailto:mailto:mwaugh@stern.nyu.edu}{mwaugh@stern.nyu.edu}\\
Office: KMC 7-74\\
Phone: 212-998-0288\\
Office hours: TBA, Monday and Wednesday.

\subsubsection*{Where and When}
Meeting times: Monday and Wednesday 330-445pm\\

Meeting place: KMC 5-140

@@

\textbf{Teaching Fellows}\\
\\
Felipe Alves 
Email: \href{mailto:mailto:falves@stern.nyu.edu}{falves@stern.nyu.edu}\\
Office hours: TBA\\

Guess what\ldots you also have classmates that can help!!! You can post questions (and maybe answer your classmates questions) on our discussion group (see below). Felipe and I will also monitor the discussion group.

@@

Everything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{https://nyu.data-bootcamp.com/undergrad_outline/}
\end{center}
\vspace{-0.15in}
%
The {\bf book\/} has its own site,
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.
We will not use NYU Classes.

We have set up {\bf announcement and discussion groups\/} (Google groups)
to make announcements and post questions. We will use this to post all assignments and
answer keys.
If you have coding or other questions, we encourage you to post them there.
If you know the answer to someone else's question, we {\bf strongly } encourage you to post that, too.
The links are
\vspace{-0.1in}
\begin{center}
\url{https://groups.google.com/d/forum/databootcamp_fall2017_undergrad} 
\end{center}
\vspace{-0.1in}
You can access the same links from the course website.  Follow the instructions to join under whatever email address you plan to use.

@@

The course divides naturally into two parts.
The first part is an introduction to those aspects of the Python programming language
useful for data analysis.
We cover this material with as many applications to real data as we can think of.
It ends with an exam.
The second part covers advanced topics and ends with a project of your own.
The goal is for you to have a piece of work you can show potential employers to
illustrate your quantitative skill set.
Both parts include a number of graded deliverables.
The idea is to {\bf do some work all the time rather than lots of work once in a while.}
We don't believe the latter will work.

Graded work includes:
%
\begin{itemize}

\item {\bf Code Practice.\/}
There are three such assignments in the first month.
We encourage you do to all of them --- they're good practice ---
but your grade will be based on the best two. We find that people who finish these assignments
tend to keep up with the material better and these are easy points to get in terms of grades.
We will also distribute Optional Code Practice ``assignments,''
but they will not be collected or graded.
They are, however, a good way to develop your coding skills.

@@

\item {\bf Examination.\/}
The exam will cover material from the first half of the course.
It takes 75 minutes and will be held in class.
It will involve coding.
{\bf Bring your computer.\/}
We suggest you also {\bf bring one page of notes\/}.
If the internet is working you will be able to look things up on there.
If not, your notes will save you.
It's also a good study tool:  When you decide what to include,
you'll be organizing your thoughts about what you've learned.

\item {\bf Project.\/}
We work our way up to the project one step at a time, starting with idea generation and ending
with a {\bf professional piece of data collection and analysis\/}
that you can share with potential employers.
The structure of the project is laid out in a separate document. We have found that the quality
of final project had a surprisingly low correlation to previous programming experience. A little thought and
effort go a long way in creating an interesting project.

@@

{\bf Due dates} are posted on the course website.
Assignments, whether code practice or components of the project,
are due at the start of class on the specified dates.

@@

{\bf Final grades\/} will be computed from
\begin{center}
\begin{tabular}{ll}
Code Practice (best two of three) & 20\% \\
Exam        & 30\% \\
Project     & 50\% \\
\end{tabular}
\end{center}

Final grades are not subject to any fixed distribution or curve.
The number of A grades, for example,
will depend only on your performance in the course.
If you make a good-faith effort,
we expect it to be hard to get less than a B.
We are the sole judges of what constitutes good-faith effort.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp}
\runningheader{Data Bootcamp}{}{Syllabus: ECON-UB.0232}
\runningfooter{}{}{}

\begin{document}
\centerline{\Large\bf Syllabus:  Data Bootcamp}
\vspace{3mm}
\centerline{\large\bf ECON-UB.0232 $|$ Spring 2018}
\vspace{3mm}
\centerline{\bf Revised:  \today}

@@

\subsubsection*{About the Instructor}
\href{http://www.waugheconomics.com}{Professor Michael Waugh} \\
Email: \href{mailto:mailto:mwaugh@stern.nyu.edu}{mwaugh@stern.nyu.edu}\\
Office: KMC 7-74\\
Phone: 212-998-0288\\
Office hours: TBA

\subsubsection*{Where and When}
Meeting times: Tuesday and Thursday 11am-12:15pm

Meeting place: KMC 3-70

\subsection*{Important Dates}

\begin{itemize}

\item Mini-Midterm \#1: February 22nd, 2018. Quick info: Python fundamentals 1-2, 30 minutes, in class, open book, open internet if the wireless is up, bring one page of notes.

\item Mini-Midterm \#2: March 22nd, 2018. Quick info: Intro to Pandas and Matplotlib, 30 minutes, in class, open book, open internet if the wireless is up, bring one page of notes.

\item Three Project Ideas: March 29, 2018. Jupyter Notebook with three project ideas, briefly flushed out and potential data sources. Hard copy due at 5pm.

\item Final Project Proposal + Data Report: April 20th, 2018. Jupyter Notebook with final proposal. More details to be provided. Hard copy due at 5pm.

\item Final Project Due Date: End of Day May 14, 2018

@@

\textbf{Teaching Fellows}\\
\\
Vineetha Kutty \\
Email: \href{mailto:vkk242@nyu.edu}{vkk242@nyu.edu}\\
Office hours: TBA\\

@@

Everything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{https://nyu.data-bootcamp.com/undergrad_outline/}
\end{center}
\vspace{-0.15in}

\textbf{Note we will NOT use NYU Classes.}

The {\bf book\/} has its own site,
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.

@@

The course divides naturally into three parts. 
\begin{itemize}
\item The first part is an introduction to basic aspects of the Python programming language. The mini-midterm \#1 covers this material.
\item The second part covers data analysis aspects of Python. The key tools we will learn about are Pandas and Matplotlib. We cover this material with as many applications to real data as we can think of. The mini-midterm \#2 covers this material.
\item The third covers advanced topics (mostly advanced functionality of Pandas and visualization) and ends with a project of your own. The ultimate goal is for you to have a piece of work you can show potential employers to illustrate your quantitative skill set.
\end{itemize}
All parts include a number of graded deliverables. The idea is to {\bf do some work all the time rather than lots of work once in a while.} We don't believe the latter will work.

Graded work includes:
\begin{itemize}

\item {\bf Code Practice.\/}
There are four such assignments in the first month and a half. We encourage you do to all of them|they're good practice|but your grade will be based on the best three. We find that people who finish these assignments tend to keep up with the material better and these are easy points to get in terms of grades.

@@

\item {\bf Exams.\/}
There will be two ``mini'' exams. These exams are mini in the sense that they are only 30 minutes long. It will involve coding. {\bf Bring your computer.\/} It will be open book, open internet if the wireless is up. We suggest you also {\bf bring one page of notes\/}.
If the internet is working you will be able to look things up on there.
If not, your notes will save you.
It's also a good study tool:  When you decide what to include,
you'll be organizing your thoughts about what you've learned.

\item {\bf Project.\/}
We work our way up to the project one step at a time, starting with idea generation and ending
with a {\bf professional piece of data collection and analysis\/}
that you can share with potential employers. We have found that the quality
of final project had a surprisingly low correlation to previous programming experience. A little thought and
effort go a long way in creating an interesting project.

@@

{\bf Due dates} are posted on the course website.

@@

{\bf Final grades\/} will be computed from
\begin{center}
\begin{tabular}{ll}
Participation / Professionalism & 5\% \\
Code Practice (best three of four) & 15\% \\
Exam \#1        & 15\% \\
Exam \#2        & 15\% \\
Project     & 50\% \\
\end{tabular}
\end{center}

Final grades are not subject to any fixed distribution or curve. The number of A grades, for example, will depend only on your performance in the course.

@@

\section*{Professional Behavior}
In the interest of having a high-quality experience for all, your classmates and I ask that you:
\begin{itemize}
\item Attend. They say ``eighty percent of success is just showing up.'' I see it often, those who show up perform systematically better.

\item Arrive to class on time and stay to the end of the class period. Chronically arriving late or leaving class early is unprofessional and disruptive to the entire class.

\item Eating or drinking in class in any way that interferes with class decorum is inappropriate.

\item Be respectful to myself, the teaching fellow, and your classmates.

\item Join your classmates. Avoid the last row. Be Engaged!
\end{itemize}
